% ************************************************************
% REPLICATION APPENDIX
% ************************************************************

\appendix
\section{Replication Appendix}
\label{app:replication}

\subsection{Repository and workflow}
\label{app:repository-workflow}

The manuscript evidence package is generated from the public repository workflow. The current primary manuscript evidence configuration is \texttt{configs/experiment\_64rep.json}. The weak-control sensitivity configuration is \texttt{configs/experiment\_weak\_controls\_64rep.json}. The alternate-seed robustness configuration is \texttt{configs/experiment\_weak\_controls\_seed\_robustness\_64rep.json}. Smaller smoke-test configurations are used only for engineering validation and are not treated as manuscript-scale evidence.

The recommended full workflow command is:

\begin{verbatim}
./scripts/run_segmented.sh full --strict --python .venv/bin/python \
  --config configs/experiment_weak_controls_seed_robustness_64rep.json
\end{verbatim}

The corresponding validation and evidence commands are:

\begin{verbatim}
.venv/bin/python scripts/08_validate_artifact_coherence.py \
  --config configs/experiment_weak_controls_seed_robustness_64rep.json
.venv/bin/python scripts/09_validate_artifact_consistency.py \
  --config configs/experiment_weak_controls_seed_robustness_64rep.json
.venv/bin/python scripts/10_effect_size_tables.py \
  --config configs/experiment_weak_controls_seed_robustness_64rep.json
.venv/bin/python scripts/12_run_external_randomness.py --allow-missing-dieharder
.venv/bin/python scripts/09_build_evidence_register.py \
  --config configs/experiment_weak_controls_seed_robustness_64rep.json \
  --output docs/evidence_register_weak_controls_seed_robustness.md
\end{verbatim}

\subsection{Eligibility criteria for manuscript evidence}
\label{app:evidence-eligibility}

A run is eligible for manuscript evidence only if artifact-coherence validation passes and the generated backend summary confirms manuscript-grade persistent-homology backends such as \texttt{ripser} or \texttt{gudhi\_cubical}. Any run containing \texttt{fallback\_threshold\_graph} is excluded from manuscript claims. H1 figures are eligible only when the corresponding backend and embedding produce finite H1 intervals. Distance-to-baseline figures are eligible only when the table identifies the configured baseline condition and the interpretation reflects that baseline.

\subsection{Registered evidence files}
\label{app:registered-evidence-files}

The current thesis scope is supported by three evidence-register files:

\begin{itemize}
  \item \texttt{docs/evidence\_register.md}
  \item \texttt{docs/evidence\_register\_weak\_controls.md}
  \item \texttt{docs/evidence\_register\_weak\_controls\_seed\_robustness.md}
\end{itemize}

Each evidence register records the artifact paths, validation status, observed backends, external randomness-test status, generated figures, and generated logs. The external randomness-test table may be schema-only until Dieharder, NIST SP 800-22, or another external suite has been run and imported.

\subsection{Required artifacts}
\label{app:required-artifacts}

The replication package requires stream manifests, embedding manifests, backend summaries, topological feature summaries, distance-to-baseline tables, internal randomness diagnostics, and imported external randomness-test outputs where available. For the seed-robustness 64-replicate run, the registered artifact scale is 512 streams, 1,024 embeddings, 2,048 TDA feature rows, 512 internal randomness rows, 0 external randomness rows, 4 backend-summary rows, 32 feature-summary rows, and 2,048 distance-to-baseline rows.

\subsection{Claim traceability checklist}
\label{app:claim-traceability-checklist}

Before a result claim is added to the manuscript, the following checklist should be satisfied:

\begin{enumerate}
  \item The claim names the relevant configuration file.
  \item The claim identifies the baseline condition when using distance-to-baseline summaries.
  \item The claim is supported by a registered table, figure, validation log, or evidence register.
  \item The backend status is manuscript-grade and no fallback backend is used for the claim.
  \item The claim does not imply cipher breaking, vulnerability discovery, or security certification.
  \item External randomness-test claims are made only if an external test table is populated by a completed external run.
\end{enumerate}

\subsection{Interpretive limits}
\label{app:interpretive-limits}

The analysis is a diagnostic comparison of topological and statistical summaries under controlled stream-generation conditions. It does not constitute a cryptanalytic attack, a proof of cipher security, or a replacement for formal analysis of AES, Ascon, DES, TDEA, or any other cryptographic primitive. Any future extension to additional ciphers, embeddings, or external test batteries should be registered as a separate evidence block before being used for thesis claims.
