% ************************************************************
% THESIS STATUS SCAFFOLD
% ************************************************************

\section{Thesis Status and Claim Boundary}
\label{sec:thesis-status}

The empirical scope is now sufficient for a defensible methods/results thesis centered on reproducible topological diagnostics. The completed evidence base includes a six-condition 64-replicate internal run, an eight-condition weak-control sensitivity extension, and an alternate-seed robustness check. Each run is documented by an evidence register that records configuration, validation status, artifact scale, backend status, external-test availability, registered figures, and registered logs.

The thesis claim should remain conservative. The supported claim is that registered persistent-homology summaries can reproducibly distinguish deliberately structured weak-control byte streams from a SHA-256 seeded deterministic baseline under the configured byte-pair and sliding-window embeddings. The evidence does not support a cipher break, an AES vulnerability claim, a practical cryptanalytic attack, security certification, or completed local Dieharder comparison.

The remaining thesis work is manuscript construction rather than additional internal TDA experimentation. The next writing tasks are to freeze empirical scope, curate final tables and figures from registered artifacts, write methods around the object-oriented workflow and validation gates, write results around the three registered evidence runs, and preserve limitations language around external randomness testing and cryptanalytic non-claims.
